---
title: "Alcohol vs Seat choice"
author: "Gloria Jones"
date: "Summer2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

The boxplot indicates the back row is higher than the front and middle.  Over 75% of people who sit in the back consume more than the individuals sitting in the middle and front. 
    
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

After observing this data plot we may reject the null hypothesis. There is a difference in how much people drink depending on where they're sitting. The red dots are outliers. Whiskers extend one and a hald times the box.  
  
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The back shows it is different because the mean is 9.6, The middle row is 6.3, and the front row is the lowest with 1.8.
  
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
  
We will reject the null hypothesis, but we will look for further clarification on which rows were different from the other rows.  
  
## Conclusions


