---
title: "Alcohol vs Seat choice"
author: "Gloria Jones"
date: "Summer2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

The boxplot indicates the back row is higher than the front and middle.  Over 75% of people who sit in the back consume more than the individuals sitting in the middle and front. 
    
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

After observing this data plot we may reject the null hypothesis. There is a difference in how much people drink depending on where they're sitting. The red dots are outliers. Whiskers extend one and a hald times the box.  
  
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The back shows it is different because the mean is 9.6, The middle row is 6.3, and the front row is the lowest with 1.8.
  
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
  
We will reject the null hypothesis, but we will look for further clarification on which rows were different from the other rows.  

```{r}
plot(TukeyHSD(model1))
```
  
The Turkey box plot tells us that the front is in fact different from the back, and the middle is different from the back. However, there is a difference between the middle and the front.  
  
## Conclusions
  
The results of the categorical variable has more than 2 levels, we had to use anova, not a t-test. The anova showed there was a difference in alcohol consumption where the individuals were seated. We were still unsure about the results, so we had to do further investigation by using the turkey HSD. It showed that there was a  difference in the back row, and not much difference compared in the middle and front.
  
